Optimizing Abstract Abstract Machines

### 2013-07-01 paper/paper.tex
Funding acknowledgements.

>>>>

We thank our anonymous reviewers for their detailed comments. This
material is based on research sponsored by DARPA under the programs
Auto- mated Program Analysis for Cybersecurity (FA8750-12-2- 0106) and
Clean-Slate Resilient Adaptive Hosts (CRASH).  The U.S. Government is
authorized to reproduce and dis- tribute reprints for Governmental
purposes notwithstanding any copyright notation thereon.
